17th International Satisfiability Modulo Theories Competition (SMT-COMP 2022): Rules and Procedures

### 2022-05-26 rules/rules22.tex
Added missing dates.
Benchmark Deadline was in March (according to SMT-COMP website)
NYSE is July 5th, since July 4th is a holiday.

\begin{description}
\item[TDB] Deadline for new benchmark contributions.
\item[May~28] Final versions of competition tools (e.g., benchmark
  scrambler) are made available.  Benchmark libraries are frozen.
\item[June~18] Deadline for first versions of solvers (for all tracks),
  including information about which tracks and divisions are being
  entered, and magic numbers for benchmark scrambling.
\item[July~2] Deadline for final versions of solvers, including
  system descriptions.
\item[TDB] Opening value of NYSE Composite Index used to compute
  random seed for competition tools.
\item[August 11/12] SMT Workshop; end of competition, presentation of
  results.
\end{description}

>>>>

\begin{description}
\item[Mar~15] Deadline for new benchmark contributions.
\item[May~28] Final versions of competition tools (e.g., benchmark
  scrambler) are made available.  Benchmark libraries are frozen.
\item[June~18] Deadline for first versions of solvers (for all tracks),
  including information about which tracks and divisions are being
  entered, and magic numbers for benchmark scrambling.
\item[July~2] Deadline for final versions of solvers, including
  system descriptions.
\item[July~5] Opening value of NYSE Composite Index used to compute
  random seed for competition tools.
\item[August 11/12] SMT Workshop; end of competition, presentation of
  results.
\end{description}
